---
title: "Generate Captive Motor Insurance Data"
author: "Mick Cooney <mickcooney@gmail.com"
date: "24 September 2017"
output:
  html_document:
    toc: true
    number_sections: true
    fig_caption: yes
    theme: cerulean
  pdf_document: default
---


```{r knit_opts, include = FALSE}
rm(list = ls())

library(tidyverse)
library(scales)
library(cowplot)
library(feather)


options(width = 80
       ,warn  = 1
        )


knitr::knit_hooks$set(timeit = local({
    now = NULL
  
    function(before, options) {
        if(before) {
            now <<- Sys.time()
        } else {
            res = difftime(Sys.time(), now)
            now <<- NULL
      
            # use options$label if you want the chunk label as well
            message('Time for this code chunk: ', as.character(res %>% round(3)))
        }
    }
}))


knitr::opts_chunk$set(tidy   = FALSE
                     ,cache  = FALSE
                     ,timeit = TRUE
                     ,message = FALSE
                     ,warning = FALSE
                     ,fig.height =  8
                     ,fig.width  = 11
                     )

#source("custom_functions.R")

set.seed(42)
```

# Initialise Country of Operations

```{r setup_country_data, echo=TRUE}
data_snapshot_date <- as.Date('2017-06-30')

loglogistic_func <- function(t, om, th) 1 - exp(-(t/th)^om)
weibull_func     <- function(t, om, th) t^om / (t^om + th^om)


bi_params_country_dev_tbl <- tribble(
    ~country_code,    ~ll_om, ~ll_th, ~wb_om, ~wb_th, ~mix_mu, ~mix_k, ~dev_sd
   ,        "DEU",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "FRA",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "GBR",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "IRL",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "ESP",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "ITA",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "NLD",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "BEL",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "AUT",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "POL",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "PRT",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "SWE",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
   ,        "DNK",      1.50,   2.50,   3.00,   1.50,     0.5,     10,    0.30
)

pd_params_country_dev_tbl <- tribble(
    ~country_code,    ~ll_om, ~ll_th, ~wb_om, ~wb_th, ~mix_mu, ~mix_k, ~dev_sd
   ,        "DEU",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "FRA",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "GBR",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "IRL",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "ESP",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "ITA",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "NLD",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "BEL",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "AUT",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "POL",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "PRT",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "SWE",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
   ,        "DNK",      0.75,   0.25,   2.50,   1.25,     0.5,     10,    0.30
)

claim_rate_country_input_tbl <- tribble(
    ~country_code, ~year, ~rate_mu, ~rate_sd
   ,        "DEU",  2000,     0.25,     0.05
   ,        "DEU",  2010,     0.30,     0.05
   ,        "DEU",  2018,     0.20,     0.05
   ,        "FRA",  2000,     0.20,     0.05
   ,        "FRA",  2018,     0.20,     0.05
   ,        "GBR",  2000,     0.20,     0.05
   ,        "GBR",  2010,     0.20,     0.05
   ,        "GBR",  2018,     0.15,     0.05
   ,        "IRL",  2000,     0.25,     0.05
   ,        "IRL",  2010,     0.20,     0.05
   ,        "IRL",  2018,     0.30,     0.05
   ,        "ESP",  2000,     0.20,     0.05
   ,        "ESP",  2018,     0.20,     0.05
   ,        "ITA",  2000,     0.20,     0.05
   ,        "ITA",  2018,     0.20,     0.05
   ,        "NLD",  2000,     0.20,     0.05
   ,        "NLD",  2018,     0.20,     0.05
   ,        "BEL",  2000,     0.20,     0.05
   ,        "BEL",  2018,     0.20,     0.05
   ,        "AUT",  2000,     0.30,     0.05
   ,        "AUT",  2018,     0.20,     0.05
   ,        "POL",  2000,     0.35,     0.05
   ,        "POL",  2018,     0.25,     0.05
   ,        "PRT",  2000,     0.20,     0.05
   ,        "PRT",  2018,     0.20,     0.05
   ,        "SWE",  2000,     0.20,     0.05
   ,        "SWE",  2018,     0.20,     0.05
   ,        "DNK",  2000,     0.20,     0.05
   ,        "DNK",  2018,     0.20,     0.05
)


country_vehicle_adjust_tbl <- tribble(
    ~country_code,   ~adj_factor
   ,        "DEU",          1.00
   ,        "FRA",          0.80
   ,        "GBR",          1.25
   ,        "IRL",          1.00
   ,        "ESP",          0.90
   ,        "ITA",          0.75
   ,        "NLD",          1.10
   ,        "BEL",          1.00
   ,        "AUT",          1.00
   ,        "POL",          0.50
   ,        "PRT",          0.85
   ,        "SWE",          1.00
   ,        "DNK",          1.00
    
)

claim_split_country_input_tbl <- tribble(
    ~country_code, ~year, ~bi_prop,  ~bi_only
   ,        "DEU",  2000,     0.25,      0.10
   ,        "DEU",  2018,     0.20,      0.10
   ,        "FRA",  2000,     0.20,      0.10
   ,        "FRA",  2018,     0.20,      0.10
   ,        "GBR",  2000,     0.25,      0.10
   ,        "GBR",  2018,     0.35,      0.10
   ,        "IRL",  2000,     0.25,      0.10
   ,        "IRL",  2018,     0.40,      0.10
   ,        "ESP",  2000,     0.20,      0.10
   ,        "ESP",  2018,     0.20,      0.10
   ,        "ITA",  2000,     0.20,      0.10
   ,        "ITA",  2018,     0.20,      0.10
   ,        "NLD",  2000,     0.20,      0.10
   ,        "NLD",  2018,     0.20,      0.10
   ,        "BEL",  2000,     0.20,      0.10
   ,        "BEL",  2018,     0.20,      0.10
   ,        "AUT",  2000,     0.30,      0.10
   ,        "AUT",  2018,     0.20,      0.10
   ,        "POL",  2000,     0.35,      0.10
   ,        "POL",  2018,     0.25,      0.10
   ,        "PRT",  2000,     0.20,      0.10
   ,        "PRT",  2018,     0.20,      0.10
   ,        "SWE",  2000,     0.20,      0.10
   ,        "SWE",  2018,     0.20,      0.10
   ,        "DNK",  2000,     0.20,      0.10
   ,        "DNK",  2018,     0.30,      0.10
)

claim_size_pd_country_input_tbl <- tribble(
    ~country_code, ~year, ~size_mu, ~size_sd, ~size_rt
   ,        "DEU",  2000,     2000,     0.10,    0.001
   ,        "DEU",  2018,     3000,     0.10,    0.002
   ,        "FRA",  2000,     2000,     0.10,    0.001
   ,        "FRA",  2018,     3000,     0.10,    0.001
   ,        "GBR",  2000,     2000,     0.10,    0.001
   ,        "GBR",  2018,     4000,     0.10,    0.001
   ,        "IRL",  2000,     2000,     0.10,    0.001
   ,        "IRL",  2010,     3000,     0.10,    0.001
   ,        "IRL",  2018,     3500,     0.10,    0.001
   ,        "ESP",  2000,     1500,     0.10,    0.001
   ,        "ESP",  2018,     2500,     0.10,    0.001
   ,        "ITA",  2000,     2000,     0.10,    0.001
   ,        "ITA",  2018,     3000,     0.10,    0.001
   ,        "NLD",  2000,     1500,     0.10,    0.001
   ,        "NLD",  2018,     2000,     0.10,    0.001
   ,        "BEL",  2000,     1000,     0.10,    0.001
   ,        "BEL",  2018,     2000,     0.10,    0.001
   ,        "AUT",  2000,     1000,     0.10,    0.001
   ,        "AUT",  2018,     2000,     0.10,    0.001
   ,        "POL",  2000,      500,     0.10,    0.001
   ,        "POL",  2018,     1000,     0.10,    0.001
   ,        "PRT",  2000,     1000,     0.10,    0.001
   ,        "PRT",  2018,     1500,     0.10,    0.001
   ,        "SWE",  2000,     2000,     0.10,    0.001
   ,        "SWE",  2018,     3000,     0.10,    0.001
   ,        "DNK",  2000,     1000,     0.10,    0.001
   ,        "DNK",  2018,     2500,     0.10,    0.001
)

claim_size_bi_country_input_tbl <- tribble(
    ~country_code, ~year, ~size_mu, ~size_sd, ~size_rt
   ,        "DEU",  2000,     3000,     0.40,   0.0001
   ,        "DEU",  2018,     5000,     0.40,   0.0002
   ,        "FRA",  2000,     3000,     0.40,   0.0001
   ,        "FRA",  2018,     5000,     0.40,   0.0001
   ,        "GBR",  2000,     3000,     0.40,   0.0001
   ,        "GBR",  2018,     6000,     0.40,   0.0001
   ,        "IRL",  2000,     4000,     0.40,   0.0001
   ,        "IRL",  2010,     5000,     0.40,   0.0001
   ,        "IRL",  2018,     8000,     0.40,   0.0001
   ,        "ESP",  2000,     2000,     0.40,   0.0001
   ,        "ESP",  2018,     3000,     0.40,   0.0001
   ,        "ITA",  2000,     3000,     0.40,   0.0001
   ,        "ITA",  2018,     4000,     0.40,   0.0001
   ,        "NLD",  2000,     2000,     0.40,   0.0001
   ,        "NLD",  2018,     3000,     0.40,   0.0001
   ,        "BEL",  2000,     2000,     0.40,   0.0001
   ,        "BEL",  2018,     3000,     0.40,   0.0001
   ,        "AUT",  2000,     2000,     0.40,   0.0001
   ,        "AUT",  2018,     3000,     0.40,   0.0001
   ,        "POL",  2000,      500,     0.40,   0.0001
   ,        "POL",  2018,     1000,     0.40,   0.0001
   ,        "PRT",  2000,     1000,     0.40,   0.0001
   ,        "PRT",  2018,     2000,     0.40,   0.0001
   ,        "SWE",  2000,     3000,     0.40,   0.0001
   ,        "SWE",  2018,     4000,     0.40,   0.0001
   ,        "DNK",  2000,     3000,     0.40,   0.0001
   ,        "DNK",  2018,     4000,     0.40,   0.0001
)

```


# Create Country Data

```{r construct_data_generation_tables, echo=TRUE}
data_country_code <- c(bi_params_country_dev_tbl$country_code
                      ,pd_params_country_dev_tbl$country_code) %>%
    sort %>%
    unique

data_min_year <- c(claim_rate_country_input_tbl$year
                  ,claim_size_bi_country_input_tbl$year
                  ,claim_size_pd_country_input_tbl$year
                  ) %>% min

data_max_year <- c(claim_rate_country_input_tbl$year
                  ,claim_size_bi_country_input_tbl$year
                  ,claim_size_pd_country_input_tbl$year
                  ) %>% max
```


```{r project_future_populations, echo=TRUE}
global_pop_tbl <- read_csv("data/global_pop.csv", skip = 4, col_types = cols()) %>%
    rename(country_name   = `Country Name`
          ,country_code   = `Country Code`
          ,indicator_name = `Indicator Name`
          ,indicator_code = `Indicator Code`
           ) %>%
    select(-X62) %>%
    gather('year','value', -country_name, -country_code, -indicator_name
          ,-indicator_code) %>%
    mutate(year  = year  %>% as.numeric
          )

country_pop_tbl <- global_pop_tbl %>%
    filter(year >= data_min_year
          ,country_code %in% data_country_code)

pop_proj_2017_tbl <- country_pop_tbl %>%
    filter(year == 2016) %>%
    mutate(year = 2017
          ,value = (value * 1.02) %>% round(0) %>% as.integer)
 
pop_proj_2018_tbl <- country_pop_tbl %>%
    filter(year == 2016) %>%
    mutate(year = 2018
          ,value = (value * 1.05) %>% round(0) %>% as.integer)

new_country_pop_tbl <- list(country_pop_tbl
                           ,pop_proj_2017_tbl
                           ,pop_proj_2018_tbl) %>%
    bind_rows()
```

Now that we have populations for the countries of interest and projected those
forward for the next few years, we use these populations to calculate the 
vehicle counts.


```{r calculate_vehicle_exposures, echo=TRUE}
n_entries <- new_country_pop_tbl %>% nrow

country_vehicle_tbl <- new_country_pop_tbl %>%
    left_join(country_vehicle_adjust_tbl, by = 'country_code') %>%
    mutate(vehicles = (value * adj_factor * runif(n_entries, 8e-5, 1e-4)) %>%
                        round(0) %>%
                        as.integer
           ) %>%
    select(country_code, year, vehicles)


interp_yearly_params <- function(year, val_label, x_vals) {
    interp_vals <- approx(x = year, y = x_vals, xout = data_min_year:data_max_year)

    data_frame(year = interp_vals$x, label = val_label, value = interp_vals$y)
}

country_claim_params_tbl <- claim_size_bi_country_input_tbl %>%
    left_join(claim_size_pd_country_input_tbl
             ,by     = c('country_code','year')
             ,suffix = c('_bi','_pd')) %>%
    left_join(claim_split_country_input_tbl, by = c('country_code', 'year')) %>%
    left_join(claim_rate_country_input_tbl,  by = c('country_code', 'year')) %>%
    group_by(country_code) %>%
    summarise(pd_mu = list(interp_yearly_params(year, 'size_mu_pd', size_mu_pd))
             ,pd_sd = list(interp_yearly_params(year, 'size_sd_pd', size_sd_pd))
             ,pd_rt = list(interp_yearly_params(year, 'size_rt_pd', size_rt_pd))
             ,bi_mu = list(interp_yearly_params(year, 'size_mu_bi', size_mu_bi))
             ,bi_sd = list(interp_yearly_params(year, 'size_sd_bi', size_sd_bi))
             ,bi_rt = list(interp_yearly_params(year, 'size_rt_bi', size_rt_bi))
             ,bi_prop = list(interp_yearly_params(year, 'bi_prop', bi_prop))
             ,bi_only = list(interp_yearly_params(year, 'bi_only', bi_only))
             ,rate_mu = list(interp_yearly_params(year, 'rate_mu', rate_mu))
             ,rate_sd = list(interp_yearly_params(year, 'rate_sd', rate_sd))
        ) %>%
    mutate(data = pmap(list(pd_mu, pd_sd, pd_rt, bi_mu, bi_sd, bi_rt
                           ,bi_prop, bi_only, rate_mu, rate_sd)
                      ,bind_rows)) %>%
    select(country_code, data) %>%
    unnest %>%
    spread('label', 'value')
```

```{r plot_vehicle_exposures, echo=TRUE, fig.height = 14}
ggplot(country_vehicle_tbl) +
    geom_line(aes(x = year, y = vehicles)) +
    expand_limits(y = 0) +
    facet_wrap(~country_code, scales = 'free_y', ncol = 2) +
    scale_y_continuous(labels = comma) +
    xlab("Year") +
    ylab("Vehicle Count")
```


# Generate Country Claim Data


## Generate Count Data

```{r generate_country_claim_counts, echo=TRUE}
claim_simtable_tbl <- country_claim_params_tbl %>%
    left_join(country_vehicle_tbl, by = c('country_code','year')) %>%
    mutate(claimcount_mu = rate_mu * vehicles
          ,claimcount_sd = rate_sd * vehicles
          ,claim_count = map2_int(claimcount_mu, claimcount_sd
                                 ,function(mu, sd) rnorm(1, mu, sd) %>% round(0) %>% as.integer)
           )

```

We now look at the line trends of the claim counts.

```{r plot_claim_counts, echo=TRUE, fig.height = 14}
ggplot(claim_simtable_tbl) +
    geom_line(aes(x = year, y = claim_count)) +
    expand_limits(y = 0) +
    facet_wrap(~country_code, scales = 'free_y', ncol = 2) +
    scale_y_continuous(labels = comma) +
    xlab("Year") +
    ylab("Claim Counts")
```

## Generate Claim Size

```{r generate_claim_size, echo=TRUE}
generate_claim_data <- function(n_claims, bi_prop, bi_only, bi_mu, bi_rt, bi_sd, pd_mu, pd_rt, pd_sd) {
    
    day_offset <- sample(1:365, n_claims, replace = TRUE)
    
    mu_vals <- pd_mu * rlnorm(n_claims, 0, pd_sd)
    rt_vals <- pd_rt * rlnorm(n_claims, 0, pd_sd)

    pd_claim_size <- map2_dbl(mu_vals * rt_vals, rt_vals, function(x, y) rgamma(1, x, y))

    mu_vals <- bi_mu * rlnorm(n_claims, 0, bi_sd)
    rt_vals <- bi_rt * rlnorm(n_claims, 0, bi_sd)

    bi_claim_size <- map2_dbl(mu_vals * rt_vals, rt_vals, function(x, y) rgamma(1, x, y))

    bi_flag <- sample(c(1,0), n_claims, prob = c(bi_prop, 1-bi_prop), replace = TRUE)
    pd_flag <- sample(c(0,1), n_claims, prob = c(bi_only, 1-bi_only), replace = TRUE)    

    bi_amount <- bi_claim_size * bi_flag
    pd_amount <- pd_claim_size * (!bi_flag | (bi_flag & pd_flag)) 

    claim_tbl <- data_frame(
        day_offset   = day_offset
       ,pd_amount    = pd_amount %>% round(2)
       ,bi_amount    = bi_amount %>% round(2)
       ,total_amount = (pd_amount + bi_amount) %>% round(2)
    )

    return(claim_tbl)
}

claim_data_tbl <- claim_simtable_tbl %>%
    mutate(size_data = pmap(list(n_claims = claim_count
                                ,bi_prop  = bi_prop
                                ,bi_only  = bi_only
                                ,bi_mu    = size_mu_bi
                                ,bi_rt    = size_rt_bi
                                ,bi_sd    = size_sd_bi
                                ,pd_mu    = size_mu_pd
                                ,pd_rt    = size_rt_pd
                                ,pd_sd    = size_sd_pd
                                )
                           ,generate_claim_data)) %>%
    select(country_code, year, size_data) %>%
    unnest %>%
    mutate(incident_date = as.Date(paste0(year, '-01-01')) + day_offset
          ,ym_label      = format(incident_date, '%Y%m')
           ) %>%
    arrange(country_code, year, incident_date) %>%
    group_by(country_code, ym_label) %>%
    mutate(claim_id = sprintf("%s%sCL%04d", country_code, ym_label, 1:n())) %>%
    ungroup() %>%
    select(country_code, year, incident_date, claim_id, pd_amount, bi_amount, total_amount)
```

Now that we have generated the ultimate claim amounts we want to take a quick
plot of the claim amounts to see how big they are.

```{r plot_ultimate_claim_sizes, echo=TRUE, fig.height=14}
ggplot(claim_data_tbl) +
    geom_histogram(aes(x = total_amount), bins = 50) +
    facet_wrap(~country_code, scales = 'free_y', ncol = 2) +
    scale_x_continuous(labels = comma) +
    xlab("Claim Amount") +
    ylab("Count")
```


# Create Claims Transactions

```{r create_claim_transaction_generation, echo=TRUE}
create_transaction_function <- function(params_tbl, time_vals) {
    
    create_transactions <- function(use_code, claim_amount) {
        
        if(claim_amount <= 1e-6) {
            dev_tbl <- data_frame()
        } else {
            use_tbl <- params_tbl %>% filter(country_code == use_code)
        
            param_noise <- rlnorm(4, 0, 0.2)
            
            ll_om <- use_tbl$ll_om * param_noise[1]
            ll_th <- use_tbl$ll_om * param_noise[2]
            wb_om <- use_tbl$wb_om * param_noise[3]
            wb_th <- use_tbl$wb_th * param_noise[4]
    
            mix_mu <- use_tbl$mix_mu
            mix_k  <- use_tbl$mix_k
            
            dev_sd <- use_tbl$dev_sd
            
            ll_dev_fact <- loglogistic_func(time_vals, ll_om, ll_th)
            wb_dev_fact <- weibull_func    (time_vals, wb_om, wb_th)
    
            mix <- rbeta(1, mix_mu * mix_k, (1-mix_mu) * mix_k)
            
            dev_fact <- (ll_dev_fact * mix) + (wb_dev_fact * (1-mix))
            
            cdf_samp <- c(1, 1 - runif(20)) %>% cumprod
            cdf_samp <- 1 - cdf_samp
    
            dev_times <- approx(x = dev_fact, y = time_vals, xout = cdf_samp)
            
            transactions_tbl <- data_frame(
                time     = dev_times$y
               ,cuml_dev = dev_times$x
               ,amount   = dev_times$x * claim_amount
            )
    
            n_keep <- transactions_tbl %>%
                filter(cuml_dev <= 0.95) %>%
                nrow
    
            n_keep <- n_keep+1
            
            dev_tbl <- transactions_tbl %>%
                arrange(cuml_dev) %>%
                head(n_keep) %>%
                mutate(amount = amount * rlnorm(n_keep, 0, dev_sd))
    
            dev_tbl$amount[n_keep] <- claim_amount
    
            dev_tbl <- dev_tbl %>%
                filter(time > 0) %>%
                select(time, amount)
        }
        
                
        return(dev_tbl)
    }
    
    return(create_transactions)
}

generate_pd_development <- create_transaction_function(pd_params_country_dev_tbl, 0:120 / 12)
generate_bi_development <- create_transaction_function(bi_params_country_dev_tbl, 0:120 / 12)
```


```{r create_claim_development_data, echo=TRUE}
claim_dev_data_tbl <- claim_data_tbl %>%
    mutate(pd_dev = map2(country_code, pd_amount, generate_pd_development)
          ,bi_dev = map2(country_code, bi_amount, generate_bi_development)
           )

pd_trans_tbl <- claim_dev_data_tbl %>%
    select(claim_id, incident_date, pd_dev) %>%
    unnest %>%
    mutate(claim_type = 'PD')

bi_trans_tbl <- claim_dev_data_tbl %>%
    select(claim_id, incident_date, bi_dev) %>%
    unnest %>%
    mutate(claim_type = 'BI')

claim_transactions_tbl <- list(pd_trans_tbl, bi_trans_tbl) %>%
    bind_rows() %>%
    mutate(transaction_date = incident_date + time * 365) %>%
    select(claim_id, incident_date, transaction_date, claim_type, amount)
```


# Create Data Snapshots

```{r take_data_snapshot, echo=TRUE}
snapshot_vehicle_tbl <- country_vehicle_tbl %>%
    filter(as.Date(paste0(year, '-01-01')) <= data_snapshot_date)

snapshot_transaction_tbl <- claim_transactions_tbl %>%
    filter(transaction_date <= data_snapshot_date)
```



# Write to Disk

```{r write_data, echo=TRUE}
write_csv(country_vehicle_tbl,    path = 'output/vehicle_counts.csv')
write_csv(claim_data_tbl,         path = 'output/claim_data_tbl.csv')
write_csv(claim_transactions_tbl, path = 'output/claim_transactions.csv')

write_feather(country_vehicle_tbl,    path = 'output/vehicle_counts.feather')
write_feather(claim_data_tbl,         path = 'output/claim_data.feather')
write_feather(claim_transactions_tbl, path = 'output/claim_transactions.feather')

### Write data snapshot
write_csv(snapshot_vehicle_tbl,     path = 'output/snapshot_vehicle.csv')
write_csv(snapshot_transaction_tbl, path = 'output/snapshot_transaction.csv')

write_feather(snapshot_vehicle_tbl,     path = 'output/snapshot_vehicle.feather')
write_feather(snapshot_transaction_tbl, path = 'output/snapshot_transaction.feather')
```
